On the application of microwave acoustic resonant viral inactivation \thanks{I would be delighted to include any criticisms or comments anyone may have; preferably leave them on the GitHub issues page, or email therobotist@gmail.com, @0xDBFB7 on Twitter, or irc.0xDBFB7.com:6667 \#covid.}

### 2020-07-21 documents/paper.tex
Microfluidic
Improved FDTD sim
Yaaaaaaay microfluidics

The chain of literature 
%
\cite{Longrange1968} \textrightarrow \ \cite{Biological1980} \textrightarrow \ [Liu 2009] \textrightarrow \ ([Hung 2014] $\parallel$ [Yang 2015] $\parallel$ [Sun 2017])\footnote{We have not conducted a thorough review; many more papers are probably involved.} apparently culminates in the flagship work we focus on in this paper,

{\it Efficient Structure Resonance Energy Transfer from Microwaves to Confined Acoustic Vibrations in Viruses} [Yang 2015].
%

@@

\lettrine{It} cannot be overstated how unexpected and positively dubious this finding appears to be -at least, based on our limited research and experience to date.

For even the RF power limits set by standards organizations appear to be based on the observation that no significant resonance modes exist in biological tissues, and (as we shall see), this is grounded in solid {\it in vitro} (albeit more limited {\it in vivo}) evidence.

@@

The precise structure and charge of the virion appears to be a singular anomaly in this otherwise catagorical non-existence.

@@

\footnote{All values have been converted to $\text{W/m}^2$ to avoid confusion. 100 $\text{ W/m}^2 = 10 \text{ mW/cm}^2 = 10 \text{ dBm/cm}^2$.}

@@

@@

@@

To drive home this point, apparently the best-quality evidence available fulfills sham requirements [Vijayalaxmi 2006] provide in-vitro. They expose blood lymphocytes to pulse power in precisely the regime required in this work; 8.2 GHz, 8 ns duration and 50 khz repetition rate, a whopping pulse power density of 250,000 $\text{W/m}^2$\footnote{computed from average power / duty cycle} (2500x the time-averaged power density safety limit), average power density 100 $\text{W/m}^2$ (the safety limit), for 2 hours, finding no change in any of the measured quantities.

Simlarly, [Chemeris 2004] use 8.8 GHz, 180 ns pulse width, peak power 65,000 W, repetition rate 50 Hz, exposure duration 40 min, on frog etheyrocytes, and find genotoxicity only from the temperature rise.

@@

@@

@@

@@

SARS is found widely distributed throughout many of the most favoured organs [Ding 2004], shielded by an average of 4 cm of chest wall [Schroeder 2013]; so safe external treatment of the body is unlikely.

@@

@@

\paragraph{}

@@

@@

>>>>

The chain of literature 
%
\cite{Longrange1968} \textrightarrow \ \cite{Biological1980} \textrightarrow \ \cite{Microwave2009} \textrightarrow \ (\cite{focusing2014} $\parallel$ \cite{Efficient2015} $\parallel$ \cite{Resonant2017})\footnote{We have not conducted a thorough review; many more papers are probably involved.} apparently culminates in the flagship work we focus on in this paper,

{\it Efficient Structure Resonance Energy Transfer from Microwaves to Confined Acoustic Vibrations in Viruses} \cite{Efficient2015}.
%

@@

\lettrine{It} cannot be overstated how unexpected and positively dubious this finding appears to be - that is, based on our limited research and inexperience to date.

For even the RF power limits set by standards organizations like \cite{ICNIRP2020} \cite{IEEE2006} appear to be based on the observation that no significant resonance modes exist in biological tissues due to damping forces from the surrounding tissue \cite{Vibrational2002}. As we shall see, this is grounded in solid {\it in vitro} (albeit more limited {\it in vivo}) evidence.

@@

The precise structure and charge of the virion appears to be a singular anomaly in this otherwise categorical non-existence.

@@

\footnote{All values have been converted to $\text{W/m}^2$ to avoid confusion. 100 $\text{W/m}^2 = 10 \text{ mW/cm}^2 = 10 \text{ dBm/cm}^2$.}

@@

\begin{table} 
	\centering
	\begin{threeparttable}
		\caption{Safety limits from various standards}
		\begin{tabular}{lllll}
			\toprule
			Stubhead & \( df \) & \( f \) & \( \Wsqm \) & \( p \) \\
			\midrule
			&     \multicolumn{4}{c}{Spanning text}     \\
			Row 1    & 1        & 0.67    & 0.55       & 0.41    \\
			Row 2    & 2        & 0.02    & 0.01       & 0.39    \\
			Row 3    & 3        & 0.15    & 0.33       & 0.34    \\
			Row 4    & 4        & 1.00    & 0.76       & 0.54    \\
			\bottomrule
		\end{tabular}
		\begin{tablenotes}
			\small
			\item This is where authors provide additional information about
			the data, including whatever notes are needed.
		\end{tablenotes}
	\end{threeparttable}
\end{table}

All pertinent restrictions for frequency $<$ 6 GHz, for general public.
ICNIRP 2020, Table 2, "Basic restrictions for electromagnetic field exposure",
20 \Wsqm, averaged over a 6 min period, averaged over a square $4 \text{cm}^2$ surface area of the body.

Whole-body average SAR $<$ 0.08 W/kg

And, additionally,

ICNIRP 2020, Table 3, Basic Restrictions

@@

Note that contrary to the limits at lower frequencies, neither ICNIRP nor IEEE appear to explicitly specify a maximum electric field; only the maximum power is specified (thereby implicitly restricting the electric field magnitude).

@@

To drive home this point, apparently the best-quality evidence available fulfills sham requirements provide in-vitro. They expose blood lymphocytes to pulse power in precisely the regime required in this work; 8.2 GHz, 8 ns duration and 50 khz repetition rate, a whopping pulse power density of 250,000 $\text{W/m}^2$\footnote{computed from average power / duty cycle} (2500x the time-averaged power density safety limit), average power density 100 $\text{W/m}^2$ (the safety limit), for 2 hours, finding no change in any of the measured quantities.

Similarly, [Chemeris 2004] use 8.8 GHz, 180 ns pulse width, peak power 65,000 W, repetition rate 50 Hz, exposure duration 40 min, and find genotoxicity purely due to the temperature rise.

@@

Moreover, 
\begin{quote}

In the absence of publication bias, since the sampling error is random, all studies will be distributed symmetrically around the mean d value.

@@

\clearpage
{\Large \it The plausibility of low-cost microwave masks}\\

With the most recent few generations of semiconductor processes, producing significant powers in the X-band has become inexpensive. Silicon transistors are limited in their output power and gain; Silicon-on-insulator topologies

This is perhaps most readily illustrated with the HB100 radar module. This device implements a complete doppler radar with two RF MOSFETS and a dielectric resonator. It operates at 10.6 GHz, yet are produced for under \$3. The PCB is stock FR4.

Our crude experimentation has yielded about 10 mW with a single SiGe:C transistor, the Infineon BFP620 (\$ 0.34 apiece \@ 1000-of.). For the personal microwave sterilizer, given the threshold levels found by Yang, this corresponds to a cost per sterilized cubic centimeter of approx. \cite{BFP620H7764XTSA1}.

@@

The mechanism restricts the possible modes of application; it would be useful to

@@

SARS is found widely distributed throughout many of the most favoured organs \cite{Organ2004}, shielded by an average of 4 cm of chest wall [Schroeder 2013]; so safe external treatment of the body is unlikely.

@@

{\color{red} speculation \{ }

@@

@@

{\color{red} speculation \} }

@@

\clearpage
\paragraph{}

### 2020-07-21 documents/supplemental.tex
Yaaaaaaay microfluidics

There seems to be a discrepancy between [Yang 2015] and our reading of [C95.1-2005].

They use a threshold in open public space of $100(f/3)^{1/5} \text{ W/m}^2$. The 115 W @ 6 GHz they provide correctly corresponds to this equation with a coefficient of 100.

@@

@@

@@

>>>>

There seems to be a discrepancy between \cite{Efficient2015} and our reading of [C95.1-2005].

They use a threshold in open public space of $100(f/3)^{1/5} \text{ W/m}^2$. The 115 W @ 6 GHz figure they provide corresponds to this equation with a coefficient of 100.

@@

We did not discover how little of an effect a wideband sweep would have until late in the project; for this reason, much of the below caters towards wideband circuits and could be greatly simplified for single-frequency operation.

@@

\printbibliography[heading=none, title={}, keyword={amplifier}]

@@

\printbibliography[heading=none, title={}, keyword={rectifier}]
